Dynamique des communautés

### 2025-04-21 Article_BIO500/Article_BIO500.Rmd
acknowledgment vers biblio

# Méthode

@@

<!-- Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references-->
\showmatmethods
\showacknow
\pnasbreak

>>>>

# Méthodes

@@

# Bibliographie {-}
<!-- Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references-->
\pnasbreak
